Action alternatives & confidence factor

### 2023-08-09 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/action_alternatives_confidence_factor.Rmd
Update action_alternatives_confidence_factor.Rmd

# action alternatives - count
describeBy(main$count, main$id)
plot_action_count <- boxplot(count ~ id, data = main)

# action alternatives - non disruptive alternatives  
describeBy(main$percent_nd, main$id)
plot_action_quality <- boxplot(percent_nd ~ id, data = main)

@@

### action alternatives non-disruptive
# t-test for expertise differences
t.test(x = main$percent_nd[main$id == "Expert"],
       y = main$percent_nd[main$id == "Novice"])

@@

# novices: correlation between confidence factor and non-disruptive alternatives
nov_confi_nd_corr <- cor.test(corr.nov$confidence_factor,
                              corr.nov$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_confi_nd_corr, 
      short = F)

# experts: correlation between confidence factor and non-disruptive alternatives
exp_confi_nd_corr <- cor.test(corr.exp$confidence_factor,
                              corr.exp$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_confi_nd_corr,
      short = F)

# full sample: correlation between confidence factor and non-disruptive alternatives
full_confi_nd_corr <- corr.test(main$confidence_factor, 
                                main$percent_nd, method=c("pearson"),
                                adjust="holm")
print(full_confi_nd_corr,
      short = F)

@@

# novices: correlation between count and non-disruptive alternatives
nov_count_nd_corr <- cor.test(corr.nov$count,
                              corr.nov$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_count_nd_corr, 
      short = F)

# experts: correlation between count and non-disruptive alternatives
exp_count_nd_corr <- cor.test(corr.exp$count,
                              corr.exp$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_count_nd_corr,
      short = F)

# full sample: correlation between confidence factor and non-disruptive alternatives
full_count_nd_corr <- corr.test(main$count, 
                                main$percent_nd, 
                                method=c("pearson"),
                                adjust="holm")
print(full_count_nd_corr,
      short = F)

>>>>

# action alternatives - count
describeBy(main$count, main$id)
plot_action_count <- boxplot(count ~ id, data = main)^

# action alternatives - non disruptive alternatives (sum score)
describeBy(main$nd, main$id)
plot_action_quality <- boxplot(nd ~ id, data = main)

# action alternatives - non disruptive alternatives (relative score)
describeBy(main$percent_nd, main$id)
plot_action_quality <- boxplot(percent_nd ~ id, data = main)

@@

### action alternatives non-disruptive absolute score
# t-test for expertise differences
t.test(x = main$nd[main$id == "Expert"],
       y = main$nd[main$id == "Novice"])

# effect size for expertise differences
CohenD(x = main$nd[main$id == "Expert"],
       y = main$nd[main$id == "Novice"],
       na.rm = TRUE)

### action alternatives non-disruptive relative score
# t-test for expertise differences
t.test(x = main$percent_nd[main$id == "Expert"],
       y = main$percent_nd[main$id == "Novice"])

@@

# novices: correlation between confidence factor and non-disruptive alternatives (absolute score)
nov_confi_abs.nd_corr <- cor.test(corr.nov$confidence_factor,
                              corr.nov$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_confi_abs.nd_corr, 
      short = F)

# experts: correlation between confidence factor and non-disruptive alternatives (absolute score)
exp_confi_abs.nd_corr <- cor.test(corr.exp$confidence_factor,
                              corr.exp$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_confi_abs.nd_corr,
      short = F)

# full sample: correlation between confidence factor and non-disruptive alternatives (absolute score)
full_confi_abs.nd_corr <- corr.test(main$confidence_factor, 
                                main$nd, method=c("pearson"),
                                adjust="holm")
print(full_confi_abs.nd_corr,
      short = F)

@@

# novices: correlation between confidence factor and non-disruptive alternatives (relative score)
nov_confi_nd_corr <- cor.test(corr.nov$confidence_factor,
                              corr.nov$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_confi_nd_corr, 
      short = F)

# experts: correlation between confidence factor and non-disruptive alternatives (relative score)
exp_confi_nd_corr <- cor.test(corr.exp$confidence_factor,
                              corr.exp$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_confi_nd_corr,
      short = F)

# full sample: correlation between confidence factor and non-disruptive alternatives (relative score)
full_confi_nd_corr <- corr.test(main$confidence_factor, 
                                main$percent_nd, method=c("pearson"),
                                adjust="holm")
print(full_confi_nd_corr,
      short = F)

# novices: correlation between count and non-disruptive alternatives (absolute score)
nov_count_abs.nd_corr <- cor.test(corr.nov$count,
                              corr.nov$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_count_abs.nd_corr, 
      short = F)

# experts: correlation between count and non-disruptive alternatives (absolute score)
exp_count_abs.nd_corr <- cor.test(corr.exp$count,
                              corr.exp$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_count_abs.nd_corr,
      short = F)

# full sample: correlation between confidence factor and non-disruptive alternatives (absolute score)
full_count_abs.nd_corr <- corr.test(main$count, 
                                main$nd, 
                                method=c("pearson"),
                                adjust="holm")
print(full_count_abs.nd_corr,
      short = F)

# novices: correlation between count and non-disruptive alternatives (relative score)
nov_count_nd_corr <- cor.test(corr.nov$count,
                              corr.nov$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_count_nd_corr, 
      short = F)

# experts: correlation between count and non-disruptive alternatives (relative score)
exp_count_nd_corr <- cor.test(corr.exp$count,
                              corr.exp$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_count_nd_corr,
      short = F)

# full sample: correlation between confidence factor and non-disruptive alternatives (relative score)
full_count_nd_corr <- corr.test(main$count, 
                                main$percent_nd, 
                                method=c("pearson"),
                                adjust="holm")
print(full_count_nd_corr,
      short = F)
